An Aliasing-Tolerant Parallel Programming Model

### 2012-11-13 doc/types-pldi2013/intro.tex
intro

In this work, we present the static and dynamic semantics for Legion \cite{Legion12},
a parallel programming model that supports multiple, dynamic data partitions and is
able to efficiently reason about potential aliasing.
Legion's {\em logical regions} are an abstraction that captures {\em locality} 
(data that will be used together, and therefore should be colocated) 
and {\em independence} (disjoint data that may be operated on in parallel).  
Logical regions have properties that allow programmers to communicate information
about the structure of program data to the Legion implementation:
\begin{itemize}
\item  logical regions are first-class values in Legion
and may be dynamically allocated and stored in data structures;

>>>>

In this work, we present static and dynamic semantics for Legion  \cite{Legion12},
a parallel programming model that supports multiple, dynamic data partitions and is
able to efficiently reason about potential aliasing.
Legion's {\em logical regions} are an abstraction that captures {\em locality} 
(data that will be used together, and therefore should be colocated) 
and {\em independence} (disjoint data that may be operated on in parallel).  
Logical regions have properties that allow programmers to communicate information
about the structure of program data to the Legion implementation:
\begin{itemize}
\item  logical regions are first-class values in Legion
and may be dynamically allocated and stored in data structures;
